# Codebook for Getting and Cleaning Data Project

This codebook was created on `r as.character(Sys.time())`.

* [Variable list and descriptions](## Variable list and descriptions)
* [Dataset structure](## Dataset structure)
* [Some data from the output](## Some data from the output)
* [Summary of variables](## Summary of variables)
* [Save data to file](## Save data to file)

## Variable list and descriptions

Variable name    | Description
-----------------|------------
Activity         | Activity name
Subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
Unit             | Feature: Time domain signal or frequency domain signal (Time or Freq)
Device           | Feature: Measuring instrument (Accelerometer or Gyroscope)
Originator       | Feature: Originator for acceleration signal (Body or Gravity)
Jerk             | Feature: Jerk signal logic (True or False)
Magnitude        | Feature: Magnitude of the signals calculated using the Euclidean norm, logic(True or False)
Axis             | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
Mean             | Feature: Average mean values
Std              | Feature: Average standard deviation values

## Dataset structure

```{r}
str(shrink.data)
```

## Some data from the output

```{r}
shrink.data
```

## Summary of variables

```{r}
summary(shrink.data)
```

## Save data to file

Save data table objects to a tab-delimited text file called `data.txt`.

```{r save}
write.table(shrink.data, file = "tidydata.txt", row.names = F)
```